Check experimental design

### 2023-05-04 analysis/01_experimental-design.Rmd
Included an index-coded design and set of interaction terms

```{r load-data, warning=FALSE, message=FALSE}
library(tidyverse)
library(donorheuristics)
library(fastDummies)
library(here)

@@

# Use dummy_cols() to get a index-coded version of all the attribute levels.
dummy_design <- dummy_cols(
  dummy_design,
  select_columns = c("org", "issue", "transp", "account", "fund", "gov_rel"),
  remove_first_dummy = TRUE,
  remove_selected_columns = TRUE
)

# Rename the index variables.
colnames(dummy_design)[4:15] <- c(
  str_c("org", 2:4), str_c("issue", 2:4), str_c("transp", 2),
  str_c("account", 2), str_c("fund", 2:3), str_c("gov_rel", 2:3)
)

@@

# Interactions

@@

```{r interactions, warning=FALSE, message=FALSE}
# Convert the attributes in design into factors
interactions <- as.data.frame(design)
for(i in 4:ncol(interactions)) {
  interactions[,i] <- as.factor(interactions[,i])
}

@@

# Use dummy_cols() to get a dummy-coded version of all the attribute levels.
interactions <- dummy_cols(
  interactions, 
  select_columns = c("org", "issue", "transp", "account", "fund", "gov_rel"),
  remove_first_dummy = FALSE,
  remove_selected_columns = TRUE
)

# Rename the dummy-coded variables.
colnames(interactions)[4:21] <- c(
  str_c("org", 1:4), str_c("issue", 1:4), str_c("transp", 1:2), 
  str_c("account", 1:2), str_c("fund", 1:3), str_c("gov_rel", 1:3)
)

# Build out all the necessary interactions.

@@

# Save interact-coded design output
write.csv(interactions, here("data", "derived_data", "interactions.csv"))
```

>>>>

```{r load-data, warning=FALSE, message=FALSE}
library(tidyverse)
library(fastDummies)
library(here)

@@

# Use dummy_cols() to get a dummy-coded version of all the attribute levels
dummy_design <- dummy_cols(
  dummy_design,
  select_columns = c("org", "issue", "transp", "account", "fund", "gov_rel"),
  remove_first_dummy = TRUE,
  remove_selected_columns = TRUE
)

# Rename the index variables
colnames(dummy_design)[4:15] <- c(
  str_c("org", 2:4), str_c("issue", 2:4), str_c("transp", 2),
  str_c("account", 2), str_c("fund", 2:3), str_c("gov_rel", 2:3)
)

@@

# Dummy-coded interactions

@@

```{r dummy-interactions, warning=FALSE, message=FALSE}
# Convert the attributes in design into factors
interactions <- as.data.frame(design)
for(i in 4:ncol(interactions)) {
  interactions[,i] <- as.factor(interactions[,i])
}

@@

# Use dummy_cols() to get a dummy-coded version of all the attribute levels
interactions <- dummy_cols(
  interactions, 
  select_columns = c("org", "issue", "transp", "account", "fund", "gov_rel"),
  remove_first_dummy = FALSE,
  remove_selected_columns = TRUE
)

# Rename the dummy-coded variables
colnames(interactions)[4:21] <- c(
  str_c("org", 1:4), str_c("issue", 1:4), str_c("transp", 1:2), 
  str_c("account", 1:2), str_c("fund", 1:3), str_c("gov_rel", 1:3)
)

# Build out all the necessary interactions

@@

# Save interact-coded design output
write.csv(interactions, here("data", "derived_data", "dummy_interactions.csv"))
```

# Index-code the design

Now we prepare the experimental design for use in estimating the model by keeping each level of each attribute, which are all discrete. An index-coded design has no reference levels.

```{r index-design, warning=FALSE, message=FALSE}
# Convert the attributes in design into factors
index_design <- as.data.frame(design)
for(i in 4:ncol(index_design)) {
  index_design[,i] <- as.factor(index_design[,i])
}

# Rename the variables.
colnames(index_design)[4:9] <- c("org", "issue", "transp", "account", "fund", "gov_rel")

# Use dummy_cols() to get an index-coded version of all the attribute levels
index_design <- dummy_cols(
  index_design,
  select_columns = c("org", "issue", "transp", "account", "fund", "gov_rel"),
  remove_first_dummy = FALSE,
  remove_selected_columns = TRUE
)

# Rename the index-coded variables
colnames(index_design)[4:21] <- c(
  str_c("org", 1:4), str_c("issue", 1:4), str_c("transp", 1:2), 
  str_c("account", 1:2), str_c("fund", 1:3), str_c("gov_rel", 1:3)
)

# Save index-coded design output
write.csv(index_design, here("data", "derived_data", "index_design.csv"))
```

# Index-coded interactions

```{r index-interactions, warning=FALSE, message=FALSE}
# Convert the attributes in design into factors
interactions <- as.data.frame(design)
for(i in 4:ncol(interactions)) {
  interactions[,i] <- as.factor(interactions[,i])
}

# Rename the variables
colnames(interactions)[4:9] <- c("org", "issue", "transp", "account", "fund", "gov_rel")

# Use dummy_cols() to get an index-coded version of all the attribute levels
interactions <- dummy_cols(
  interactions, 
  select_columns = c("org", "issue", "transp", "account", "fund", "gov_rel"),
  remove_first_dummy = FALSE,
  remove_selected_columns = TRUE
)

# Rename the index-coded variables
colnames(interactions)[4:21] <- c(
  str_c("org", 1:4), str_c("issue", 1:4), str_c("transp", 1:2), 
  str_c("account", 1:2), str_c("fund", 1:3), str_c("gov_rel", 1:3)
)

# Build out all the necessary interactions
    emergency_criticized = issue1 * gov_rel2,
    emergency_crackdown = issue1 * gov_rel3,
    smalldonors_criticized = fund1 * gov_rel2,
    smalldonors_crackdown = fund1 * gov_rel3,
    emergency_smalldonors_crackdown = issue1 * fund1 * gov_rel3,
    environment_smalldonors_crackdown = issue2 * fund1 * gov_rel3,
    humanrights_smalldonors_crackdown = issue3 * fund1 * gov_rel3,
    refugees_smalldonors_crackdown = issue4 * fund1 * gov_rel3,
    nottransp_criticized = transp1 * gov_rel2,
    nottransp_crackdown = transp1 * gov_rel3,
    nottransp_smalldonors_criticized = transp1 * fund1 * gov_rel2,
    nottransp_wealthydonors_criticized = transp1 * fund2 * gov_rel2,
    nottransp_govgrants_criticized = transp1 * fund3 * gov_rel2,
    nottransp_smalldonors_crackdown = transp1 * fund1 * gov_rel3,
    nottransp_wealthydonors_crackdown = transp1 * fund2 * gov_rel3,
    nottransp_govgrants_crackdown = transp1 * fund3 * gov_rel3,
    nottransp_emergency_criticized = transp1 * issue1 * gov_rel2,
    nottransp_emergency_crackdown = transp1 * issue1 * gov_rel3,
    nottransp_environment_criticized = transp1 * issue2 * gov_rel2,
    nottransp_environment_crackdown = transp1 * issue2 * gov_rel3,
    nottransp_humanrights_criticized = transp1 * issue3 * gov_rel2,
    nottransp_humanrights_crackdown = transp1 * issue3 * gov_rel3,
    nottransp_refugees_criticized = transp1 * issue4 * gov_rel2,
    nottransp_refugees_crackdown = transp1 * issue4 * gov_rel3,
    nottransp_smalldonors_emergency_criticized = transp1 * fund1 * issue1 * gov_rel2,
    nottransp_smalldonors_emergency_crackdown = transp1 * fund1 * issue1 * gov_rel3,
    nottransp_smalldonors_environment_criticized = transp1 * fund1 * issue2 * gov_rel2,
    nottransp_smalldonors_environment_crackdown = transp1 * fund1 * issue2 * gov_rel3,
    nottransp_smalldonors_humanrights_criticized = transp1 * fund1 * issue3 * gov_rel2,
    nottransp_smalldonors_humanrights_crackdown = transp1 * fund1 * issue3 * gov_rel3,
    nottransp_smalldonors_refugees_criticized = transp1 * fund1 * issue4 * gov_rel2,
    nottransp_smalldonors_refugees_crackdown = transp1 * fund1 * issue4 * gov_rel3,
  )

# Save interact-coded design output
write.csv(interactions, here("data", "derived_data", "index_interactions.csv"))
```
